---
title: "Week 02: COVID Visualization Activity"
date: "September, 11 2023"
author: "Sungwoo Noh**"
---

Today, we'll be working with a data set related to COVID.
This data is based on data from the the [COVID Tracking Project](https://covidtracking.com/).
I cleaned up this data and also added total populations from the 2020 for each of the relevant categories.
Note, due to differences in the way race and ethnicity are encoded in the census as compared to the the COVID Tracking Project, the population counts for LatinX may be somewhat inaccurate.

```{r load_data}
library(tidyverse)
load("CRDT Data.RData")
ls()
```

I've include 4 different data sets.
They all have the same data but have it represented in different ways.
Try using the different data sets and see which ones are good for making which plots.


```{r first_plot}
ggplot(covid_data_orig, aes(x = State, y = Cases_Total)) + geom_point()
```



If you want to only look at a specific state, you can do it like this.
For now, see what you can do just using `ggplot`.

```{r}
covid_data_count |> 
  filter(state == "MA") |> 
  ggplot(aes(x = date, y = Cases, color = race)) + geom_line()
```

1. Write code for a plot and describe what you observe?

```{r}
covid_data_count|>
  filter(state=="MN")|>
ggplot(
  mapping=aes(x=Deaths,y=race))+
geom_line()

```
1. I observed line graph that has deaths as a x-axis and race as y-axis. 

2. Are there any conclusions you can draw?
White is the most race that has deaths and NHPI is the least race that has deaths in Minnesota. I can assume that the white people are likely to be exposed to corona virus han other races or majority of population in MN is white.

3. What were you not able to do due to not having the R knowledge?
I was not able to implement proper aesthetic properties such as change the angle of label, transparency, and etc.

4. What other data would be useful to better understand this data?
I believe age,gender, and poverty would be useful to better understand this data brcasue those are confounding factors that has impacts on covid-virus deaths. For example, older people are more likely to be infected with covid-19, so we can analyze the data in a different asepct and understand how the white people is the most race that died by covid-19.


